Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-08 response to reviewer.tex

\documentclass[titlepage,11pt,a4paper]{{scrartcl}}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[arrow,matrix,curve]{xy}
\usepackage[latin1]{inputenc}
\usepackage{theorem}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{a4paper,top=3cm, bottom=3cm} 
\newtheorem{satz}{Theorem}
\newtheorem{aufg}[satz]{Aufgabe}
\newtheorem{defi}[satz]{Definition}
\newtheorem{bem}[satz]{Remark}
\newtheorem{kor}[satz]{Corollary}
\newtheorem{lem}[satz]{Lemma}
\newtheorem{ver}[satz]{Conjecture}
\newtheorem{zit}[satz]{Zitat}
\newtheorem{beo}[satz]{Beobachtung}
\newtheorem{bei}[satz]{Example}
\newtheorem{pro}[satz]{Proposition}
\newcommand{\dju}{\bigcup\hspace{-2.23mm\dot}\hspace{2mm}}
\newcommand{\modu}{~\rm{mod}~}
\newcommand{\smdju}{\cup\hspace{-2.15mm\dot}\hspace{2mm}}
\newcommand\dis[1]{\bigcup_{#1}\hspace{-2.5mm\dot}\hspace{2mm}}
\newcommand{\qed}{\begin{flushright}$\square$\end{flushright}}
\newcommand\R{$\mathbb{R}$}
\newcommand\Q{$\mathbb{Q}$}
\newcommand\Z{$\mathbb{Z}$}
\newcommand\N{$\mathbb{N}$}
\newcommand\C{$\mathbb{C}$}
\newcommand\Rn{\mathbb{R}}
\newcommand\Qn{\mathbb{Q}}
\newcommand\Zn{\mathbb{Z}}
\newcommand\Nn{\mathbb{N}}
\newcommand\Cn{\mathbb{C}}
\newcommand\Sk{\langle\,\,,\,\rangle}
\newcommand{\Hom}{\mathrm{Hom}}

\newcommand{\filt}[6]{
\[
\begin{xy}
\xymatrix@R20pt@C20pt{
&\mathbb{C}^3&\\\langle #1,#2 \rangle\ar[ru]&\langle #3,#4\rangle\ar[u]&\langle #5,#6\rangle\ar[lu]\\\langle #1\rangle\ar[u]&\langle #3\rangle\ar[u]&\langle #5\rangle\ar[u]}
\end{xy}
\]
} 
\begin{document}
\pagestyle{empty}

\noindent{\bf Response to the reviewer - Cell decompositions for rank two quiver Grassmannians}\\

\noindent In the following, we point out the changes made and give responses to the referee's comments..

\renewcommand{\labelenumi}{(\arabic{enumi})}
\begin{enumerate}
  \item[Section 3.1] The referee's suggestions were incorporated into shortened proofs of Lemmas 3.4 and 3.15, and motivated a rewriting of the proof of Lemma 3.9.
  \item[Lemma 3.30] The referee's comments offer a pleasing non-inductive viewpoint towards evaluating this kernel and thus have been incorporated into a new clarified proof.
  \item[Corollary 3.32] The notation of perpendicular categories has been incorporated into the statement of the result.
  \item[Definition 3.33] We had overlooked this simple viewpoint on admissible sequences and thank the referee for these extremely helpful remarks.
    The entire section has been somewhat reorganized to better capture the nature of the construction.
  \item[After Definition 3.33] After the reorganization, this notation is no longer being used.
  \item[Before Lemma 3.34] This typo has been corrected.
  \item[Lemma 3.34] Lemma 3.34 (now 3.33) has been rewritten to clarify the inductive structure of truncated preprojectives following the change of focus onto admissible sequences.
  \item[Section 4.2] This is a matter of convention.
    In general, the placement of the $*$'s for an attracting set is equivalent to the choice of the map $d:\{1,\ldots,n\}\to\ZZ$, cells of our chosen form impose the condition $d(1)>\cdots>d(n)$.
  \item[Lemma 4.3] We have added references to Cerulli Irelli and Haupt at the beginning of Section 4.2.
    However, Haupt's statement is stronger than his proof since it assumes a thin lift to an abelian cover, a trait our representations rarely possess.
    Furthermore, it does not seem to be straightforward to obtain our explicit description of the fixed point set of the quiver Grassmannians as those subrepresentations which live on the universal abelian covering with Haupt's result. 
  \item[Section 4.4] The dependence of various Caldero-Chapoton maps on their defining sequences has been clarified.
  \item[Theorem 4.20] 
\end{enumerate}

Section 4:
\begin{enumerate}
\renewcommand{\labelenumi}{(\arabic{enumi})}
\item We inserted a remark concerning the result of Haupt. Our approach seems to simplify the language and generalize the techniques of Haupt. If we are not mistaken, the proof of Theorem 1.2(c) in Section 8 only deals with those representations of the universal (abelian) covering whose dimension vectors only consists of $0$'s and $1$'s. We actually consider arbitrary representations of $\hat Q$. Moreover, the explicit description of the fixed points of $\mathrm{Gr}_{\mathbf{e}}(M)$ of a liftable representation $M$ as subrepresentations of the lifted representations $\hat M$ seems to be missing.

\item We inserted a remark in Theorem 4.22 (former 4.20) which is meant to explain how the statement is obtained from the claim. Moreover, it should make the proof clearer.
\item I find the strategy if 4.23 is very clear and I also think that the proof of 4.24 is very close to the suggestion of the referee. Any ideas what to change?
\end{enumerate}

### 2019-06-08 Grassmannian_cells.tex
Section 3 and 4 edits, cleanup of rebuttal

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
Observe by an easy induction that $u_{k+1}-u_k>0$ for $k\ge0$ since $n\ge3$.

@@

To avoid such ambiguities, we introduce the set
\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\ne i_{j+1}\text{ for $1\le j\le k-1$}\}\subset\{1,\ldots,n\}^k\]
and call the elements of $A_1^{(k)}$ \emph{admissible sequences} of length $k$.
The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge3$, the following hold:
  \begin{enumerate}
    \item Given a decomposition $I\sqcup\{i\}=\{1,\ldots,n\}$ with $|I|=n-1$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^I\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{\tilde P_{m+1} \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.35){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.35){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
        \tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}\ar^{\tilde\pi_{m,i}^{\{i\},\{j\}^c}}[r] & \tilde P_{m,i}^{\{j\}^c}\cong \tilde P_{m-1,(i,j)}^{\{j\}}}
      \end{equation}
    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k\le m$ and any proper subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,I}:\tilde P_{m+1}\to \tilde P_{m+1-k,\ui}^I$ satisfying:
      \[\tilde\pi_{m+1}^{\ui,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I}
      \qquad\text{and}\qquad
    \tilde\pi_{m+1}^{\ui,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I\]
      for $\ell<k$, where $\ui_\ell=(i_1,\ldots,i_\ell)$ and $\ui'_\ell=(i_{\ell+1},\ldots,i_k)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

  The commutativity of the upper triangles in (2) follows from the construction of the isomorphisms in the bottom row, while the commutativity of the lower triangle is immediate from the definitions of these maps.

  These diagrams stitch together to give the composition 
  \[\tilde\pi_{m+1}^{\ui,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{\{i_1\}^c}\]
  which can be seen to satisfy the desired properties from (3) inductively using the commutativity from (2).
\qed\end{proof}

@@

The following orthogonality property is a primary reason we need to lift to the universal cover of $K(n)$.
Given $\tilde M\in\rep \tilde K(n)$, write
\[\tilde M^\perp := \{\tilde N\in\rep \tilde K(n):\Hom(\tilde M,\tilde N)=0=\Ext(\tilde M,\tilde N)\}.\]
\begin{corollary}
  \label{cor:perpendicular}
  Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
  For $m\geq 2$, we have $\tilde P_m(I,j)\in (\tilde P_{m+1}^I)^\perp$.
\end{corollary}
\begin{proof}
  If $m=2$, we have $\Hom\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$ since $\tilde P_2(I,j)$ is a direct sum of the simple projective representations $\tilde P_{1,(j,k)}$ for $k\ne j$.
  Using the explicit description of $\tilde P_3^I$ from Example~\ref{ex:truncated lifts}, we see that each $\tilde P_{1,(j,k)}$ for $k\ne j$ is supported at a vertex which is not a neighbor of the support of $\tilde P_3^I$, which implies $\Ext\!\big(\tilde P_3^I,\tilde P_{1,(j,k)}\big)=0$ for $k\neq j$ and thus $\Ext\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$.

@@

Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
We first consider a natural $\CC^*$-action on the usual Grassmannian $\Gr_k(X)$ which is compatible with a given direct sum decomposition of the vector space $X$.
Then we generalize the concept to quiver Grassmannians and observe that the $\CC^*$-fixed point sets can be calculated in an analogous manner.

@@

Assume that $X=\bigoplus_{l=1}^m X_l$ is a direct sum decomposition of $X$ and fix a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist indices $0=r_0<r_1<r_2<\cdots<r_{m-1}<r_m=n$ such that
\[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{m-1}+1},\ldots,v_{r_m}\in X_m.\]
The following lemma generalizes \cite[Theorem 1]{cerulli}.
\begin{lemma}
  \label{le:usualGrass}
  Consider a map $d:\{1,\ldots,n\}\to\ZZ$ such that $d(r)=d(r')$ if $v_r,v_{r'}\in X_l$ for some $l$ and $d(r)\neq d(r')$ if $v_r\in X_l$ and $v_{r'}\in X_{l'}$ with $l\neq l'$.
  Then under the $\CC^*$-action determined by $d$, we have $U\in\Gr_k(X)^{\C^\ast}$ if and only if $U=\bigoplus_{l=1}^m U\cap X_l$.
\end{lemma}
\begin{proof}
  Assume $U=\bigoplus_{l=1}^m U\cap X_l$.
  Then any $u\in U$ can be written uniquely as $u=\sum_{l=1}^m u_l$ for some $u_l\in U\cap X_l$.
  It follows that $t.u=\sum_{l=1}^m t.u_l=\sum_{l=1}^m t^{d(r_l)}u_l\in\bigoplus_{l=1}^m U\cap X_l=U$ and thus $t.U=U$.

@@

In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $\hat X$ if it has the properties of Lemma~\ref{le:degree condition}.
\begin{theorem}
  \label{thm:torusfixedpoints}
  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $\hat X$.
  Then the $\CC^*$-action on $\bigoplus_{i\in Q_0} X_i$ determined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a $\CC^*$-fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced $\CC^*$-actions on the usual Grassmannians of vector subspaces $\Gr_{\bfe_i}(X_i)$.
  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
  which is equivalent to $U$ being liftable to the universal abelian covering $\hat Q$.
\qed\end{proof}
\begin{remark} Note that similar techniques and results are obtained in \cite{haupt}, see e.g. \cite[Theorem 1.2(c)]{haupt}. Note that only representations $\hat X$ of $\hat Q$ are considered in the corresponding proof in \cite[Section 8]{haupt} which satisfy $\dim \hat X_{(i,\chi)}\in\{0,1\}$. Furthermore, it does not seem to be straightforward to obtain our explicit description of the fixed point set of the quiver Grassmannians as those subrepresentations which live on the universal abelian covering with Haupt's result. 
\end{remark}

@@

Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
For a fixed dimension vector $\tbfe$, this induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\begin{align*}
  \Psi:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
  E&\mapsto \big(E\cap M,(E+M)/M\big).
\end{align*}
Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.
\begin{remark}
We should always keep in mind that the middle term $B$ and the Caldero-Chapoton depend on the short exact sequence $\eta\in\Ext(N,M)$, i.e. to be more exact we should have named it $\Psi^{\eta}$. As a matter of readability we decided to omit this index.
\end{remark}
For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
\begin{equation}
  \label{eq:grassmannian decomposition}
  \Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
\end{equation}
Then $\Psi$ restricts to a map
\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
The following results are proven in \cite[Section 3]{cefr}.
For completeness we include a proof of the first.
\begin{lemma}
  \label{le:good partition}
  There exists a total ordering $\preceq$ of the dimension vectors $\tbff$ appearing in the decomposition \eqref{eq:grassmannian decomposition} such that for any fixed $\tbff$ the subset 
  \[\bigsqcup_{ \tbff'\succeq\tbff} \cG_{\tbff',\tbfe-\tbff'}\]
  is closed in $\Gr_\tbfe(B)$.
\end{lemma}
\begin{proof}
  Recall that $\Gr_\tbfe(B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(B_i)$.
  For each $i$, the inclusion $M_i\subset B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(E_i)=\dim(E_i\cap M_i)$.
  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(B_i)$.
  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\leq\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
  \[\bigsqcup_{ \tbff'\geq\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(B)\]
  for any fixed $\tbff$.
  Any refinement of this partial order to a total order $\preceq$ will give the claim.
\qed\end{proof}
\begin{theorem}
  \label{vb}
  If $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\Im\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to\Im\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
  In particular, the existence of a cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}

@@

Finally, note that the claim together with Proposition \ref{label} ensures that the fiber dimension along the points of the affine cell $C_V$ is constant. Thus Theorem \ref{vb} gives the statement of the Theorem.
\end{remark}

>>>>

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
Since $n\ge3$, we may observe by an easy induction that $u_{k+1}-u_k>0$ for $k\ge0$ and thus $u_{k+1}>(n-1)u_k$ for $k\ge0$.

@@

To avoid such ambiguities, we introduce the set
\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\ne i_{j+1}\text{ for $1\le j\le k-1$}\}\subset\{1,\ldots,n\}^k\]
and call the elements of $A_1^{(k)}$ \emph{admissible sequences} of length $k$.
The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge3$, the following hold:
  \begin{enumerate}
    \item Given a decomposition $I\sqcup\{i\}=\{1,\ldots,n\}$ with $|I|=n-1$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^I\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{\tilde P_{m+1} \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
        \tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}\ar^{\tilde\pi_{m,i}^{\{i\},\{j\}^c}}[r] & \tilde P_{m,i}^{\{j\}^c}\cong \tilde P_{m-1,(i,j)}^{\{j\}}}
      \end{equation}
    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k\le m$ and any proper subset $I\subsetneq\{1,\ldots,n\}$ with $i_k\in I$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,I}:\tilde P_{m+1}\to \tilde P_{m+1-k,\ui}^I$ satisfying:
      \[\tilde\pi_{m+1}^{\ui,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I}
      \qquad\text{and}\qquad
    \tilde\pi_{m+1}^{\ui,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I\]
      for $\ell<k$, where $\ui_\ell=(i_1,\ldots,i_\ell)$ and $\ui'_\ell=(i_{\ell+1},\ldots,i_k)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

  The commutativity of the upper triangles in (2) follows from the construction of the isomorphisms in the bottom row, while the commutativity of the lower triangle is immediate from Lemma~\ref{le:properties}.5.

  These diagrams stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
  \[\tilde\pi_{m+1}^{\ui,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{\{i_1\}^c}\]
  which can be seen to satisfy the desired properties from (3) inductively using the commutativity from (2).
\qed\end{proof}

@@

The following orthogonality property is a primary reason we need to lift to the universal cover of $K(n)$.
As usual, given $\tilde M\in\rep \widetilde{K(n)}$, we write
\[\tilde M^\perp := \{\tilde N\in\rep \widetilde{K(n)}:\Hom(\tilde M,\tilde N)=0=\Ext(\tilde M,\tilde N)\}.\]
\begin{corollary}
  \label{cor:perpendicular}
  Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
  For $m\geq 2$, we have $\tilde P_m(I,j)\in (\tilde P_{m+1}^I)^\perp$.
\end{corollary}
\begin{proof}
  If $m=2$, we have $\Hom\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$ since $\tilde P_2(I,j)$ is a direct sum of the simple projective representations $\tilde P_{1,(j,k)}$ for $k\ne j$.
  Using the explicit description of $\tilde P_3^I$ from Example~\ref{ex:truncated lifts}, we see that each $\tilde P_{1,(j,k)}$ for $k\ne j$ is supported at a vertex which is not a neighbor of the support of $\tilde P_3^I$, which implies $\Ext\!\big(\tilde P_3^I,\tilde P_{1,(j,k)}\big)=0$ for $k\neq j$ and thus $\Ext\!\big(\tilde P_3^I,\tilde P_2(I,j)\big)=0$.

@@

Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
We first consider a natural $\CC^*$-action on the usual Grassmannian $\Gr_k(X)$ which is compatible with a given direct sum decomposition of the vector space $X$.
Then we generalize the concept to quiver Grassmannians and observe that the $\CC^*$-fixed point sets can be calculated in an analogous manner.
This greatly extends the results \cite[Theorem 1]{cerulli} and \cite[Theorem 1.2]{haupt} which utilize similar constructions.

@@

Assume that $X=\bigoplus_{l=1}^m X_l$ is a direct sum decomposition of $X$ and fix a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist indices $0=r_0<r_1<r_2<\cdots<r_{m-1}<r_m=n$ such that
\[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{m-1}+1},\ldots,v_{r_m}\in X_m.\]
\begin{lemma}
  \label{le:usualGrass}
  Consider a map $d:\{1,\ldots,n\}\to\ZZ$ such that $d(r)=d(r')$ if $v_r,v_{r'}\in X_l$ for some $l$ and $d(r)\neq d(r')$ if $v_r\in X_l$ and $v_{r'}\in X_{l'}$ with $l\neq l'$.
  Then under the $\CC^*$-action determined by $d$, we have $U\in\Gr_k(X)^{\C^\ast}$ if and only if $U=\bigoplus_{l=1}^m U\cap X_l$.
\end{lemma}
\begin{proof}
  Assume $U=\bigoplus_{l=1}^m U\cap X_l$.
  Then any $u\in U$ can be written uniquely as $u=\sum_{l=1}^m u_l$ for some $u_l\in U\cap X_l$.
  It follows that $t.u=\sum_{l=1}^m t.u_l=\sum_{l=1}^m t^{d(r_l)}u_l\in\bigoplus_{l=1}^m U\cap X_l=U$ and thus $t.U=U$.

@@

In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $\hat X$ if it has the properties of Lemma~\ref{le:degree condition}.
\begin{theorem}
  \label{thm:torusfixedpoints}
  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $\hat X$.
  Then the $\CC^*$-action on $\bigoplus_{i\in Q_0} X_i$ determined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a $\CC^*$-fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced $\CC^*$-actions on the usual Grassmannians of vector subspaces $\Gr_{\bfe_i}(X_i)$.
  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
  which is equivalent to $U$ being liftable to the universal abelian covering $\hat Q$.
\qed\end{proof}

@@

Let $\eta:\ses{M}{B}{N}$ be a short exact sequence of $\widetilde{K(n)}$-representations.
For a fixed dimension vector $\tbfe$, there is an induced ``Caldero-Chapoton map'' between quiver Grassmannians
\begin{align*}
  \Psi=\Psi^\eta:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
  E&\mapsto \big(E\cap M,(E+M)/M\big).
\end{align*}
Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.
For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
\begin{equation}
  \label{eq:grassmannian decomposition}
  \Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
\end{equation}
Then $\Psi$ restricts to a map
\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
The following results are proven in \cite[Section 3]{cefr}.
For completeness we include a proof of the first.
\begin{lemma}
  \label{le:good partition}
  There exists a total ordering $\preceq$ of the dimension vectors $\tbff$ appearing in the decomposition \eqref{eq:grassmannian decomposition} such that for any fixed $\tbff$ the subset 
  \[\bigsqcup_{ \tbff'\succeq\tbff} \cG_{\tbff',\tbfe-\tbff'}\]
  is closed in $\Gr_\tbfe(B)$.
\end{lemma}
\begin{proof}
  Recall that $\Gr_\tbfe(B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(B_i)$.
  For each $i$, the inclusion $M_i\subset B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(E_i)=\dim(E_i\cap M_i)$.
  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(B_i)$.
  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\leq\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
  \[\bigsqcup_{ \tbff'\geq\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(B)\]
  for any fixed $\tbff$.
  Any refinement of this partial order to a total order $\preceq$ will give the claim.
\qed\end{proof}
\begin{theorem}
  \label{vb}
  If $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\Im\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to\Im\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
  In particular, the existence of a cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}

@@

Finally, note that the claim together with Proposition \ref{fibers} ensures that the fiber dimension along the points of the affine cell $C_V$ is constant. Thus Theorem \ref{vb} gives the statement of the Theorem.
\end{remark}
